\documentclass[defaultstyle,11pt]{thesis}

\usepackage{amsmath}
\usepackage{amssymb}		% to get all AMS symbols
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??
\usepackage{bm}
\usepackage{natbib}
\usepackage{pdfpages}

\usepackage{xcolor}
\hypersetup{
  colorlinks   = true,
  linkcolor    = gray,
  citecolor    = gray
}




%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{Fundamental Studies of Stratified Stellar Convection: Simulations and Theory}

\author{Evan~H.}{Anders}

\otherdegrees{B.S., Whitworth University, 2014 \\
	      M.S., University of Colorado, 2017}

\degree{Doctor of Philosophy}		%  #1 {long descr.}
	{Ph.D., Astrophysical \& Planetary Sciences}		%  #2 {short descr.}

\dept{Department of}			%  #1 {designation}
	{Astrophysical \& Planetary Sciences}		%  #2 {name}

%\includepdf[pages=-, pagecommand={}]{DocuSign_Evan_Anders_2020_PhD_thesis.pdf}

\advisor{Prof.}				%  #1 {title}
	{Benjamin P. Brown}			%  #2 {name}
%
%\reader{Prof.~Mark P. Rast}		%  2nd person to sign thesis
%\readerThree{Prof.~Steven Cranmer}		%  3rd person to sign thesis
%\readerFour{Prof.~Ian Grooms}
%\readerFive{Prof.~Keith Julien}
%\readerSix{Dr.~Bradley Hindman}

\abstract{  \OnePageChapter	% because it is very short, get rid of this if it goes over a page
	Convection is a ubiquitous heat transport mechanism in astrophysics and geophysics.
	In addition to transporting heat, convective motions drive a wide variety of interesting phenomena.
	In particular, the magnetic dynamos of the Earth and Sun are seated in the turbulent convective motions of their respective core and outer envelope.
	In addition to driving magnetism, convection is responsible for establishing observable mean flows, such as the Sun's differential rotation.
	The nonlinear nature of convection in the highly turbulent regime of geophysical and astrophysical settings makes its behavior difficult to predict, understand, and model.
	In this thesis, I conduct a series of experiments into the fundamental nature of convection.

	The first two of these experiments examine numerical simulations of fully compressible convection in the context of stratified atmospheres.
	From these simulations, we have learned how to study increasingly turbulent, astrophysically-interesting convection while holding the Mach number and the Rossby number (which measures the importance of the Coriolis force) constant.
	In these studies, we have learned that the fundamental heat transport mechanisms at work in simulations of stratified convection are the same as those at work in more simple, incompressible convection.

	The next two studies examine simulations of Boussinesq convection with a specific focus on understanding how simulations of convection relax over time from their initial conditions.
	In the first of these studies, we develop a simple procedure for coupling simulations with simple boundary value problems to rapidly accelerate the simulation relaxation process.
	We find very good agreement between accelerated simulations and simulations which traditionally timestep through their thermal relaxation process.
	In the second of these experiments, we show that the relaxation timescale is linked to the choice of thermal boundary conditions.
	We further show that thermal relaxation is akin to a walk through parameter space from a turbulent to more laminar regime.

	In our final study, we examine the evolution of ``thermals'' in stratified atmospheres.
	Thermals are regions of buoyant (or dense) fluid which accelerate due to their buoyancy forces and may be the fundamental unit of convection in the Earth's atmosphere.
	We develop a theory describing the evolution of thermals in stratified domains.
	This theory describes how atmospheric stratification affects buoyant entrainment of atmospheric fluid.
	We test this theory with laminar 2D and 3D simulations, and discuss implications that this work may have for stellar envelope convection.
	}

\dedication[Dedication]{	% NEVER use \OnePageChapter here.
	To Sami.
	Thanks for dealing with my late-night simulation check-ins, random stress, etc.~for (...6?) years now.

	...also, to Finn. He's adorable.
	}

\acknowledgements{	\vspace{-0.5in}\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
I'd first and foremost like to thank my family (especially Sami), my cohort (Sam [er, Soaring Eagle], Jhett, Nick, Piyush, Tristan, Jessica), and my other friends and colleagues at CU who supported me, helped me grow as a person/scientist, or just endured horrible meetings alongside me. 

I'd like to thank my mentors who have helped me grow as a scientist over the past few years.
In this, I'd especially like to thank Ben, who helped teach me to be an open-minded, careful scientist while also teaching me that it's important to balance family life.
Beyond Ben, I'm very grateful for the guidance that Jeff Oishi and Daniel Lecoanet have given me as I have navigated the thesis and postdoc process.
Outside of my academic mentors, I'd also like to thank my mentors who helped me grow as a teacher: Seth Hornstein, and the ISEE staff, especially Austin Barnes.

I'd like to thank my collaborators and co-authors.
The effort and work that Ben Brown, Jeff Oishi, Daniel Lecoanet, Geoff Vasil, Katie Manduca, and Lydia Korre put into our manuscripts vastly improved the quality of the science therein.
I'm also broadly grateful to Mark Rast, Nick Featherstone, Brad Hindman, Jon Aurnou, Nadir Jeevanjee, Ian Grooms, and Axel Brandenburg.
Discussions with all of these great scientists helped me better understand the problems I was grappling with.

For funding, I'm grateful to the APS department for funding my first year of graduate school as a teaching assistant.
I also gratefully acknowledge the support of CU's George Ellery Hale Graduate Student Fellowship, which supported me in years 2-4, and NASA Earth and Space Science Fellowship 80NSSC18K1199, which supported me in years 5-6.
I'm also broadly grateful to NASA LWS grant number NNX16AC92G, which has paid for a couple of summer salaries and has enabled travel.

Without the NASA Pleiades supercomputer, none of this work would have been possible.
Pleiades is part of the NASA High End Computing (HEC) program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center.
All computations were conducted using allocation GIDs s1647 and g26133.
	}

% \IRBprotocol{E927F29.001X}	% optional!

{\hypersetup{linkcolor=black}
\ToCisShort	% use this only for 1-page Table of Contents

\LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures

\LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input macros.tex
\input introduction.tex
\input ab17.tex
\input ro_p19.tex
\input abo18.tex
\input ft20.tex
\input alb19.tex
\input unpublished.tex

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{yahapj}	% or "siam", or "alpha", etc.
\bibliography{biblio}		% Bib database in "blblio.bib"

%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
%\appendix
%\input appendixA.tex
%\input appendixB.tex


\end{document}


%%%% Example of how to do table footnotes
%\begin{table}[htb]
%    \caption[Example of a table with its own footnotes]{
%	Here is an example of a table with its own footnotes.
%	Don't use the $\backslash${\tt footnote} macro if you
%	don't want the footnotes at the bottom of the page.
%	Also, note that in a thesis the caption goes
%	\emph{above} a table, unlike figures.
%	}
%    \begin{center}
%    \begin{tabular}{||l|c|c|c|c||} \hline
%	& $S$ & $P$ &   $Q^{\ast}$  & $D^{\dagger}$ \\	% footnote symbols!
%	wave form & (kVA) & (kW) & (kVAr) & (kVAd) \\  \hline \hline
%	Fig.  \ref{xfigDiagram}a  & 25.48 & 25.00 & -2.82 & 4.03 \\ \hline
%	Fig.  \ref{xfigDiagram}b  & 25.11 & 18.02 & -9.75 & 14.52 \\ \hline
%	Table \ref{pdftable}  & 24.98 & 22.26 & 9.19 & 6.64 \\ \hline
%	Table \ref{powertable}  & 23.48 & 15.00 & 6.59 & 16.82 \\ \hline
%	Fig.  \ref{pyramid}  & 24.64 & 22.81 & -0.44 & 9.3 \\ \hline
%	\end{tabular}
%   \\ \rule{0mm}{5mm}
%   ${}^\ast$kVAr means reactive power.		% footnote symbol
%\\ ${}^\dagger$kVAd means distortion power.	% footnote symbol
%\end{center}
%\label{powertable}
%\end{table}


