\documentclass[defaultstyle,11pt]{thesis}

\usepackage{amsmath}
\usepackage{amssymb}		% to get all AMS symbols
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??
\usepackage{bm}
\usepackage{natbib}

\usepackage{xcolor}
\hypersetup{
  colorlinks   = true,
  linkcolor    = gray,
  citecolor    = gray
}




%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{Fundamental Studies of Stratified Stellar Convection: Simulations and Theory}

\author{Evan~H.}{Anders}

\otherdegrees{B.S., Whitworth University, 2014 \\
	      M.S., University of Colorado, 2017}

\degree{Doctor of Philosophy}		%  #1 {long descr.}
	{Ph.D., Astrophysics}		%  #2 {short descr.}

\dept{Department of}			%  #1 {designation}
	{Astrophysical \& Planetary Sciences}		%  #2 {name}

\advisor{Prof.}				%  #1 {title}
	{Benjamin P. Brown}			%  #2 {name}

\reader{Prof.~Mark P. Rast}		%  2nd person to sign thesis
\readerThree{Prof.~Steven Cranmer}		%  3rd person to sign thesis
\readerFour{Prof.~Ian Grooms}
\readerFive{Prof.~Keith Julien}
\readerSix{Dr.~Bradley Hindman}

\abstract{  \OnePageChapter	% because it is very short, get rid of this if it goes over a page
		THIS IS AN ABSTRACT
	}

\dedication[Dedication]{	% NEVER use \OnePageChapter here.
	To Sami \& Finn.
	}

\acknowledgements{	\vspace{-0.5in}\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
I'd first and foremost like to thank my family (especially Sami), my cohort (Sam [er, Soaring Eagle], Jhett, Nick, Piyush, Tristan, Jessica), and my other friends and colleagues at CU (Avery, Gabo, Ryan, Katie, Tayler, Nicole, Gilly, Hayley, Jennie, many others) who supported me, helped me grow as a person/scientist, or just suffered through horrible committees and meetings with me. 

I'd like to thank my mentors who have helped me grow as a scientist over the past few years.
In this, I'd especially like to thank Ben, who helped teach me to be an open-minded, careful scientist while also teaching me that it's important to balance family life.
Beyond Ben, I'm very grateful for the guidance that Jeff Oishi and Daniel Lecoanet have given me as I navigate the thesis and postdoc process.
Outside of my academic mentors, I'd also like to thank my mentors who helped me grow as a teacher: Seth Hornstein, and the ISEE staff, especially Austin Barnes.

I'd like to thank my collaborators and co-authors.
The effort and work that Ben Brown, Jeff Oishi, Daniel Lecoanet, Geoff Vasil, and Katie Manduca put into our manuscripts vastly improved the quality of the science therein.
I'm also broadly grateful to Mark Rast, Nick Featherstone, Brad Hindman, Jon Aurnou, Nadir Jeevanjee, Ian Grooms, and Axel Brandenburg.
Discussions with all of these great scientists helped me better understand the problems I was grappling with.

For funding, I'm grateful to the APS department for funding my first year of graduate school as a teaching assistant.
I also gratefully acknowledge the support of CU's George Ellery Hale Graduate Student Fellowship, which supported me in years 2-4, and NASA Earth and Space Science Fellowship 80NSSC18K1199, which supported me in years 5-6.
I'm also broadly grateful to NASA LWS grant number NNX16AC92G, which has paid for a couple of summer salaries and has enabled quite a bit of travel.

Without the NASA Pleiades supercomputer, none of this work would have been possible.
Pleiades is part of the NASA High End Computing (HEC) program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center.
All computations were conducted using allocation GIDs s1647 and g26133.
	}

% \IRBprotocol{E927F29.001X}	% optional!

{\hypersetup{linkcolor=black}
\ToCisShort	% use this only for 1-page Table of Contents

\LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures

\LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input macros.tex
\input introduction.tex
\input ab17.tex
\input abo18.tex
\input ro_p19.tex
\input alb19.tex
\input unpublished.tex

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{yahapj}	% or "siam", or "alpha", etc.
\bibliography{biblio}		% Bib database in "blblio.bib"

%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
%\appendix
%\input appendixA.tex
%\input appendixB.tex


\end{document}


%%%% Example of how to do table footnotes
%\begin{table}[htb]
%    \caption[Example of a table with its own footnotes]{
%	Here is an example of a table with its own footnotes.
%	Don't use the $\backslash${\tt footnote} macro if you
%	don't want the footnotes at the bottom of the page.
%	Also, note that in a thesis the caption goes
%	\emph{above} a table, unlike figures.
%	}
%    \begin{center}
%    \begin{tabular}{||l|c|c|c|c||} \hline
%	& $S$ & $P$ &   $Q^{\ast}$  & $D^{\dagger}$ \\	% footnote symbols!
%	wave form & (kVA) & (kW) & (kVAr) & (kVAd) \\  \hline \hline
%	Fig.  \ref{xfigDiagram}a  & 25.48 & 25.00 & -2.82 & 4.03 \\ \hline
%	Fig.  \ref{xfigDiagram}b  & 25.11 & 18.02 & -9.75 & 14.52 \\ \hline
%	Table \ref{pdftable}  & 24.98 & 22.26 & 9.19 & 6.64 \\ \hline
%	Table \ref{powertable}  & 23.48 & 15.00 & 6.59 & 16.82 \\ \hline
%	Fig.  \ref{pyramid}  & 24.64 & 22.81 & -0.44 & 9.3 \\ \hline
%	\end{tabular}
%   \\ \rule{0mm}{5mm}
%   ${}^\ast$kVAr means reactive power.		% footnote symbol
%\\ ${}^\dagger$kVAd means distortion power.	% footnote symbol
%\end{center}
%\label{powertable}
%\end{table}


